---
title: "2020 Travelers Modeling Competition"
author: "Group 2"
date: "`r format(Sys.Date(), '%b %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r}
library(tidyverse)
library(grid)
library(gridExtra)

theme_set(theme_bw())

train_set <- read_csv("InsNova_train.csv")
test_set <- read_csv("InsNova_test.csv")
```

```{r}
colSums(is.na(train_set))
```

There are no missing values.

```{r}
grid.arrange(
  ggplot(train_set) +
    geom_histogram(aes(x = veh_value)) +
    labs(title = "market value of the vehicle in $10,000’s"),
  ggplot(train_set) +
    geom_histogram(aes(x = veh_value)) +
    scale_x_log10() +
    labs(title = "market value of the vehicle in $10,000’s (log transformed)")
)
```

The distribution of the market value of the vehicle is right skewed as shown above. Log transformation makes the distribution more symmetrical. 

```{r}
ggplot(train_set) +
  geom_histogram(aes(x = exposure)) +
  labs(title = "The basic unit of risk underlying an insurance premium")
```

The basic unit of risk underlying an insurance premium is pretty uniformly distributed between 0 and 1. 

```{r}
ggplot(train_set) +
  geom_bar(aes(x = veh_body)) +
  labs(title = "Type of vehicles") +
  coord_flip()
```

SEDAN is the most common vehicle type, and RDSTR is the least common. 

```{r}
ggplot(train_set) +
  geom_bar(aes(x = veh_age)) +
  labs(title = "Age of vehicles (1=youngest, 4=oldest)")
```

Each of the vehicle age group is pretty well-represented. 

```{r}
ggplot(train_set) +
  geom_bar(aes(x = gender)) +
  labs(title = "Gender of driver")
```

The majority of driver is female. 

```{r}
ggplot(train_set) +
  geom_bar(aes(x = area)) +
  labs(title = "Driving area of residence")
```

C is the most common area type,a nd F is the least common.

```{r}
ggplot(train_set) +
  geom_bar(aes(x = dr_age)) +
  labs(title = "Driver’s age category from young (1) to old (6)")
```

The drivers are more concentrated in the middle age groups. 

```{r}
grid.arrange(
  ggplot(train_set) +
    geom_histogram(aes(x = claim_cost)) +
    labs(title = "Claim amount"),
  ggplot(train_set) +
    geom_histogram(aes(x = claim_cost)) +
    scale_x_log10() +
    labs(title = "Claim amount (log transformed)")
)
```

There are `r sum(train_set$claim_cost==0)` policies that had 0 claim amount, which does not reflect in the log transformed graph above. 

```{r}
ggplot(train_set) +
  geom_bar(aes(x = claim_count)) +
  labs(title = "The number of claims")
```

Most policies don't have any claims. 





